\color{navyblue} Differences-in-Differences with Spatial Spillover

### 2020-12-14 latex/paper/Spillover.tex
Updated introduction and contribution

Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states. The effect of these treatments do not typically stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects affecting neighboring areas. In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that a unit's potential outcome does not depend on the treatment status of any other unit \citep{Rubin_1980}. This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g. geographic distance, node distance in a graph, or social relationships in schools or cities.}

This paper identifies problems in estimation of treatment effets in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers.

To do this, I first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}. In the presence of spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard difference-in-differences methodologies.

First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes. In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, if a factory opening in a given county benefits both that county and neighboring counties, the treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment. Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had preferences over both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units. Difference-in-differences estimation would result in double undercounting.}

Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. The spillover is added to the treated units' change in outcomes. Therefore the bias of treatment effect is the same sign as the sign of the spillover. For example a factory opening in two neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces. The estimated treatment effect will be positively biased because there is a positive spillover onto also treated units.

These biases are explicit functions of potential outcomes and can be used inuitively by researchers to sign the bias. The magnitude of the bias depends on two factors: the size of the spillover and the number of units affected by spillovers. If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large. This paper provides an explicit form for this bias and enables researchers to give bounds for it under assumptions about the size of the spillover effect and on number of units affected. I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.

Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously. In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers in their empirical specification to prevent bias in the estimation of treatment effects.

Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers. Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers on to control units. Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.

Removing both kinds of bias requires a researcher to take a stance and parameterize a functional form for the spillover function. The particular functional form depends on the context of the application however there are a few practical considerations. First, the researcher should argue whether spillovers on control units and on treated units exist. Second, they should argue what the maximum distance these spillovers can occur. Last, they should consider if spillovers are additive in the number of nearby units that are treated.

@@

There are two different models of SUTVA violations in the literature. Within-group spillovers are when units are in distinct groups and outcomes depend on the treatment status within your group only. For example, SUTVA is violated if a student's standardized test score depends on the proportion of students enrolled in a tutoring program at that school. In this case, each school constitutes a group and it is assumed treatment effect is not affected by other schools' tutoring enrollment. Estimation in this case is done in a `partial intereference' framework.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with control units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.

The more general form is sometimes called between-group spillovers which occur when groups are overlapping. For example, a counties' economic outcomes depend on the economic outcomes of nearby counties (even across state borders). Estimation in this framework is more difficult and requires the researcher to either identify control units that are free from spillovers or to parameterize how control units are affected by treatment.

\citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector. He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$. The function $h_i(\vec{D})$ is referred to as an exposure mapping and adding an exposure mapping to the potential outcomes framework allows to explicitly model SUTVA violations. Using this framework, \citet{Vazquez-Bare_2019} shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect. My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by difference-in-differences.

\citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''. Then, the authors describe how the ATE estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h_i(\vec{D})$. My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.

\citet{Delgado_Florax_2015} consider spillover only on to control units and identify a bias that can come from estimating a difference-in-differences model without explicitly controlling for spillovers. Using Monte-Carlo simulations, they find that there is an omitted variable bias problem by not including a measure of spillovers. My paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.

Similarly, \citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model. However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units. Lastly, \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} find results for a specific potential outcome function where $h_i(\vec{D})$ is the proportion of treated contiguous counties. They allow this spillover to enter the potential outcome additively and the coefficient is allowed to differ by own treatment status. In my framework, if I assume the particular functional forms for potential outcomes of \citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}, I arrive at the same bias equation as theirs.

Lastly, I contribute to a literature in urban economics on local place-based policies. Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' effects of the policy are offset in parts by indirect effects. I contribute to estimating aggregate effects of place-based policies by showing that typical estimation strategies can underestimate the local effect by ignoring spillovers. To do so, I revise the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}. The Tennessee Valley Authority was a large push to bring electrification to the Tennessee Valley with the goal of improving the manufacturing sector there. The scale of the program was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies. I show that estimation by difference-in-differences fails to account for these spillovers and underestimates the local effect.

The rest of the paper is structured as follows. Section 2 presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model. Section 3 presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature. Section 4 presents an application for evaluating the Tennessee Valley Authority program.

% ------------------------------------------------------------------------------
\section{Potential Outcomes Framework}
% ------------------------------------------------------------------------------

Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards. As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$, denoted $Y_{i,t}(D_i, h_i(\vec{D})$), are a function of own treatment-status $D_i$ and,  departing from the canonical framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$. The function $h_i(\vec{D})$ is referred to as an `exposure mapping' and is a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The `exposure mapping' measures the intensity at which unit $i$ is affected by spatial spillovers. When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = 0$. The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment and can be summarized by $h_i(\vec{D})$.

To help better understand the exposure mapping function, I give three examples of $h_i(\vec{D})$ that are commonly used in the literature. First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$ (similarly a dummy for counties that share borders is commonly used). Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.  In this case \[
    h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
\] 
This exposure mapping is useful when it is assumed that spillovers do not decay over distance and the number of neighboring units treated do not impact the intensity of spillovers. For example, this mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case the distance $\bar{d}$ would be the maximum distance people would likely travel to a nearby library. Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to the level of spillovers.

Second, $h_i(\vec{D})$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
    h_i(\vec{D}) = 1/k \sum_{j \in k(i)} D_j,
\]
where $k(i)$ is the index of unit $i$'s k-nearest neighbors. This exposure mapping is no longer binary, so intensity of spillovers depend on the number of units treated. In the context of large store openings and agglomeration economies, this would imply that as the number of nearby counties receiving new factories increase, the effect on own-county outcomes increase as well \citep{Basker_2005}.

Last, is the spatial decay function where exposure decreases with distance. This depends on the decay parameter $\alpha$ that is decided by the researcher. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \[ 
    h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
\] 
This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors.} In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure. This allows for the technology spillovers to decay over distance to an exponential degree.

The last thing a researcher must do is specify the functional form of the potential outcomes. Typically, the spillover function enters into the regression linearly and ocasionally the coefficient is allowed to differ by treatment status.

@@

With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
    Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0).
\] 
The spillover measures the difference in non-treated potential outcomes between being exposed and not being exposed at level $h_i(\vec{D})$. Then, the average spillover onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
\]

To emphasize, the average spillover onto conrol units averages over each control unit's exposure mapping. For example, assume the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$ and that the coefficient $\beta_{\text{spill,control}}$ measures the effect of $h_i(\vec{D})$ on outcome $Y$ among control units. Then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h_i(\vec{D})$. The average spillover onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E}_{i} \left[ h_i(\vec{D})\right]$, i.e. the average over all control units exposure mapping.

Similarly, we define the average spillover onto also treated units as: \[ 
    \tau_{\text{spill,treated}} \equiv \mathbb{E} \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
\]

It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences. I assume that what the `Average Treatment Effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{i}(1, 0) - Y_{i}(0, 0) \ \vert \ D_i = 1 \right],
\] 
which measures the effect of being treated in the absence of exposure to spillovers. This differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
    \mathbb{E} \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(0, h_i(\vec{D})) \ \vert \ D_i = 1 \right],
\] 
where the expectation is over individuals and their exposures. I prefer the former because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.\footnote{The spillover effects themselves might be of interest to the researcher, so clearly seperating them is beneficial in estimation. Later they can be combined to estimate the `net effects' that \citet{Sävje_Aronow_Hudgens_2019} estimate.}

@@

The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$. To show this, I first present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.

@@

When researchers run the canonical difference-in-differences regression, 
the estimate $\hat{\tau}$ will be a biased estimate for $\tau_{\text{direct}}$. Given that Assumption \ref{parallel} holds, the estimate can be decomposed as the direct effect and the two sources of spillover bias. The proof is given in Appendix \ref{sec:proofs}.

\begin{theorem}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
    If Assumption \ref{parallel} holds, the expectation of the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} is
    \begin{align*}
        \mathbb{E}[\hat{\tau}] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right]}_{\text{Difference-in-Differences}} \\ 
        &= 
        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
        &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
        &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
    \end{align*}
\end{theorem}

The intuition behind the biases are as follows. First, the change in outcomes among treated units combines the direct effect and the spillover from nearby treated units. Therefore the first difference adds the average spillover onto the treated units, $\tau_{\text{spill,treated}}$. Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover onto control units. Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover onto the control, $\tau_{\text{spill,control}}$.

Readers that are judging estimates in the presence of spillovers can use the following heuristics to size the bias. If they suspect spillovers onto control units, the bias is the opposite sign of the spillover. If they suspect spillovers onto treated units, the bias is in the same sign of the spillover. The overall bias is the sum of the two.

@@

% ------------------------------------------------------------------------------
\section{Monte Carlo Simulations}
% ------------------------------------------------------------------------------

>>>>

Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states. Potentially, the effect of these treatments do not stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects affecting neighboring areas. In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that a unit's potential outcome does not depend on the treatment status of any other unit \citep{Rubin_1980}. This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units' treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g. geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.}

This paper identifies problems in estimation of treatment effects in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers. To do this, I first introduces a potential outcome framework that explicitly models spatial spillovers following \citet{Vazquez-Bare_2019}. Typically researchers are interested in the `direct' effect on the treated units (sometimes called the partial equilibrium effect or the `local' effect). In the presence of spatial spillovers, difference-in-differences estimates identify the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.

The intuition for these two sources is as follows. First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes. In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, consider a factory opening in a county. Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain \citep{Duranton_Puga_2003}. The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment. Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had a welfare function that included both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units. Difference-in-differences estimation would result in double undercounting.}

Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. The spillover is added to the treated units' change in outcomes. Therefore the bias of treatment effect is the same sign as the sign of the spillover. Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces. The estimated treatment effect will count the `direct` effect of the factory opening as well as the benefit of the agglomeration economies. Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.

These biases are explicit functions of potential outcomes and can be used by researchers to sign or bound the bias using insight from their economic context. The magnitude of the bias depends on two factors: the size of the spillovers and the number of units affected by spillovers. If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large. This result of this paper enables researchers to give bounds for it under assumptions about the size of the spillover effect and on number of units affected. I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.

Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously. In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers in their empirical specification to prevent bias in the estimation of treatment effects. The other papers usually will first estimate the direct effect without controlling for spillovers and then later on seperately estimate the spillover effects. This paper shows that not controlling for spillovers produces biased estimates of the direct effect.

Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers. Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers onto control units. In the presence of spillover onto other treated units, the estimates will still be biased for the direct effect. Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.

Removing both sources of bias requires a researcher to take a stance and parameterize a functional form for the spillover function. The particular functional form depends on the context of the application. However, there are a few practical considerations. First, the researcher should argue whether spillovers on control units and on treated units exist. Second, they should argue what the maximum distance these spillovers can occur. Last, they should consider if spillovers are additive in the number of nearby units that are treated.

% @TODO: Discuss effectiveness under misspecification of spillovers.

@@

The literature considering spillovers primarily has focused on ``within-group'' spillovers where units are in distinct groups and outcomes depend on the treatment status within the observation's group only.\footnote{For example, researchers consider peer effects within schools. In this case, each school constitutes a group and it is assumed that outcomes do not depend on other schools' treatment status, i.e. SUTVA is satisfied between-groups. Estimation of spillover effects in this case is done in a `partial intereference' framework that compares ``control'' units in a partially treated group with control units in completely untreated groups. \citet{Angelucci_DiMaro_2016} provides a summary for estimation of spillover effects in within-group settings. Examples in the literature include: \citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} 
However, spatial settings such as counties do not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups (a county is connected to all other counties by some chain of neighbors). My paper considers a more general form of interference. Identification in this framework requires the researcher to either identify control units that are free from spillovers (far-away from treatment) or to parameterize how control units are affected by treatment.

\citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector. He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h(\vec{D}, i)$. The function $h(\vec{D}, i)$ is referred to as an exposure mapping and adding this to the potential outcomes framework allows me to explicitly model SUTVA violations. Using this framework, \citet{Vazquez-Bare_2019} shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.

My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by difference-in-differences.

\citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''. That is, a treated unit's treatment effect is defined as the direct effect and the general equilibrium spillover effects. Then, the authors describe how the ATE estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h(\vec{D}, i)$. My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.\footnote{These estimates can be combined afterwards to estimate their definition of average treatment effect. The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.}

There are a few papers that discuss estimation of treatment effects with spatial spillovers using the difference-in-differences framework. \citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model. However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units. \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} identifies biases in estimation of the direct effect for a specific potential outcome function where $h(\vec{D}, i)$ is the proportion of treated contiguous counties. Finally, \citet{Delgado_Florax_2015} consider the case where the exposure mapping is defined by a spatial weights matrix $W\vec{D}$ that enters linearly into the potential outcomes. This does not allow for the coefficient to change for control and treated units.\footnote{Although, one could change the weighting matrix to make ad-hoc assumption of the signs and relative magnitudes of spillovers onto treated and control units, but this allows for less data-driven estimation.}

My paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers. For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly.

Lastly, I contribute to a literature in urban economics on local place-based policies. Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects. I contribute to estimating aggregate effects of place-based policies by showing that typical estimation strategies can underestimate the local effect by ignoring spillovers. As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}. The Tennessee Valley Authority was a large push to bring electrification to the Tennessee Valley with the goal of improving the manufacturing sector there. The scale of the program was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies. I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.

The rest of the paper is structured as follows. Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model. Section \ref{sec:monte_carlo} presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature. Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.

% ------------------------------------------------------------------------------
\section{Potential Outcomes Framework}
\label{sec:po_framework}
% ------------------------------------------------------------------------------

Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards. As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$, denoted $Y_{i,t}(D_i, h(\vec{D}, i)$), are a function of own treatment-status $D_i$ and,  departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function. The `exposure mapping' measures the intensity at which unit $i$ is affected by spatial spillovers. When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = 0$. The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment which are summarized by $h(\vec{D}, i)$.

To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature. First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.  In this case \[
    h(\vec{D}, i) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
\] 
This exposure mapping is useful when it is assumed that spillovers do not decay over distance until $\bar{d}$ and the number of neighboring units treated do not impact the intensity of spillovers. For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library. Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to spillovers in this context.

Second, $h(\vec{D}, i)$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
    h(\vec{D}, i) = 1/k \sum_{j \in K(i)} D_j,
\]
where $K(i)$ is the index of unit $i$'s k-nearest neighbors. This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of units treated. In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies. As more nearby counties receive new factories, the agglomeration forces increase \citep{Basker_2005}.

Last, is the spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \[ 
    h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
\] 
This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be decided by the researcher or estimated using non-linear least squares. In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.

The last thing a researcher must do is specify the functional form of the potential outcomes. Typically, the spillover function enters into the regression linearly and potentially the coefficient is allowed to differ by treatment status.

@@

With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0).
\] 
The spillover measures the difference in non-treated potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed. Then, the average spillover effect onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0) \ \vert \ D_i = 0 \right].
\]

To emphasize, the average spillover effect onto conrol units averages over each control unit's exposure mapping. For example, assume the potential outcomes is additively linear in $D_i$ and $h(\vec{D}, i)$ and that the coefficient $\beta_{\text{spill,control}}$ measures the effect of $h(\vec{D}, i)$ on outcome $Y$ among control units. Then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h(\vec{D}, i)$. The average spillover effect onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E} \left[ h(\vec{D}, i)\right]$, i.e. the average over all control units exposure mapping.

Similarly, we define the average spillover effect onto also treated units as: \[ 
    \tau_{\text{spill,treated}} \equiv \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0) \ \vert \ D_i = 1 \right].
\]

It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences. I assume that what the `Average Treatment Effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, 0) - Y_{it}(0, 0) \ \vert \ D_i = 1 \right],
\] 
which measures the effect of being treated in the absence of exposure to spillovers. This effect does not include the general equilibrium effects of multiple treated areas near one-another.

My definition of the direct effect of treatment differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
    \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(0, h(\vec{D}, i)) \ \vert \ D_i = 1 \right],
\] 
where the expectation is over individuals and their exposures. I prefer the former because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves. For example, a county deciding whether to implement a policy will want to consider the treatment effect plus the spillover at their current level of exposure. The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at different levels.\footnote{Estimation of the direct effect and spillover effect can be combined to estimate the ATE as defined by \citet{Sävje_Aronow_Hudgens_2019}.}

@@

The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$ in the presence of spillovers. To show this, I first present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.

@@

Given that Assumption \ref{parallel} holds, the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} can be decomposed as the direct effect and the two sources of spillover bias. The proof is given in Appendix \ref{sec:proofs}.

\begin{theorem}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
    If Assumption \ref{parallel} holds, the expectation of the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} is
    \begin{align*}
        \mathbb{E}[\hat{\tau}] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right]}_{\text{Difference-in-Differences}} \\ 
        &= 
        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
        &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
        &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
    \end{align*}
\end{theorem}

The intuition behind the biases are as follows. First, the change in outcomes among treated units combines the direct effect and the spillover from nearby treated units. Therefore the first difference adds the average spillover effect onto the treated units, $\tau_{\text{spill,treated}}$. Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units. Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover effect onto the control, $\tau_{\text{spill,control}}$.

Readers that are judging estimates in the presence of spillovers can use the following heuristics to sign the bias. If they suspect spillovers onto control units, the bias is the opposite sign of the spillover. If they suspect spillovers onto treated units, the bias is in the same sign of the spillover. The overall bias is the sum of the two.

@@

% ------------------------------------------------------------------------------
\section{Monte Carlo Simulations}
\label{sec:monte_carlo}
% ------------------------------------------------------------------------------
